On the Evolution of Choice Principles

### 2014-07-29 text/RoaM_proceedings/paper.tex
inital export

\documentclass[10pt]{article}

@@

% \usepackage{setspace}
% \doublespacing
\usepackage[left=3.75cm,right=3.75cm,top=3.75cm,bottom=3.75cm]{geometry}

\title{On the Evolution of Choice Principles}
\author{}
\date{}

@@

\begin{center}
  \begin{large}
    On the Evolution of Choice Principles
  \end{large}
\end{center}

\noindent The widely accepted normative standard of individual decision making
under uncertainty is expected utility maximization. An agent is
rational only if his choices maximize expected utility. In games with
several players, agents who believe that their opponents are rational
might thus rule out certain of the opponents' choices. This kind of
reasoning can be iterated, giving rise to predictions of rational
choice under arbitrarily deep nestings of mutual beliefs in
rationality. % Depending on the detailed specification of what it means
% to have a belief in the opponents' rationality, and to respond
% rationally to such beliefs, standard game-theoretic solution concepts
% are characterized by this nested Theory of Mind reasoning, most
% notably the iterated deletion of strongly dominated strategies in
% strategic games \citep[e.g.][for
% overview]{Perea2012:Epistemic-Game-}.

@@

\newpage

>>>>

\documentclass{llncs}

@@

% \usepackage{setspace}
% \doublespacing
% \usepackage[left=3.75cm,right=3.75cm,top=3.75cm,bottom=3.75cm]{geometry}

\title{On the Evolution of Choice Principles}
\titlerunning{On the Evolution of Choice Principles}
\author{Michael Franke\inst{1} \and Paolo Galeazzi \inst{2}}
\institute{Department of Linguistics, University of T\"{u}bingen \and
  Institute for Logic, Language and Computation, Universiteit van Amsterdam}
\date{}

@@

\maketitle

\begin{abstract}
  We compare the evolutionary competition between different choice
  principles in arbitrary strategic games under one-shot
  interactions. Choice principles under scrutiny are level-$k$
  utility maximization and level-$k$ regret minimization. RESULTS \dots
\end{abstract}

The widely accepted normative standard of individual decision making
under uncertainty is expected utility maximization. An agent is
rational only if his choices maximize expected utility. In games with
several players, agents who believe that their opponents are rational
might thus rule out certain of the opponents' choices. This kind of
reasoning can be iterated, giving rise to predictions of rational
choice under arbitrarily deep nestings of mutual beliefs in
rationality. % Depending on the detailed specification of what it means
% to have a belief in the opponents' rationality, and to respond
% rationally to such beliefs, standard game-theoretic solution concepts
% are characterized by this nested Theory of Mind reasoning, most
% notably the iterated deletion of strongly dominated strategies in
% strategic games \citep[e.g.][for
% overview]{Perea2012:Epistemic-Game-}.

@@
